---
title: "prepare data of IV"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 July"
output:  
  md_document:
    variant: markdown_github
---
  
  
```{r wd, echo=FALSE}
#---------------------------------
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_growing_season', sep='')
#---------------------------------
```

```{r packages, warning=FALSE}
library("dplyr")
library("lubridate")
library("ggplot2")
```

## Read and prepare iv data

We created two datasets: 

* annual evi by pixel
* seasonal evi by pixel 

Each dataframe has the following fields: 

* `iv_malla_modi_id`: the identifier of the modis cell
* `year`
* `evi_mean`: the value of the evi (cumulative value for each season)
* `season`: the season of cumulative evi:
  * `0` annual value
  * `1` spring value
  * `2` summer value 
  * `3` autumn value 
  * `4` winter value 
* `seasonF`: the season coded as factor 
* `lng`: longitude coordinates
* `lat`: latitute coordinates 
* `poblacion`: numeric code of the *Q. pyrenaica* population 
  

```{r}
# Read and prepare data
rawdata <- read.csv(file=paste(di, "/data_raw/raw_iv.csv", sep= ""), header = TRUE, sep = ',')

ndvi_by_date <- rawdata %>% 
  mutate(myevi = evi * 0.0001, 
         myndvi = ndvi * 0.0001,
         yearday = lubridate::yday(fecha)) %>% 
  mutate(yearday = ifelse(yearday == 2, 3, yearday), ### Artefacto para agregar dia 2 y 3 
         monthday = as.Date(yearday - 1, origin = "2008-01-01")) %>% 
  group_by(monthday) %>% 
  summarise(mean=mean(myevi),
            sd = sd(myevi),
            se = sd / sqrt (length(myevi)))


ggplot(ndvi_by_date, aes(as.Date(monthday), y=mean)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = mean - sd, ymax= mean + sd))
  
  

xx<- rawdata %>% 
  mutate(yearday = lubridate::yday(fecha),
         yearday = ifelse(yearday == 2, 3, yearday)) %>% 
  group_by(yearday) %>% 
  summarise(con = n())
  

unique(lubridate::yday(rawdata$fecha))


dplyr::select(one_of(vnames)) %>%
    mutate_(vinterest = i) %>%
    group_by_("nie_malla_modi_id") %>%
    summarise(mean=mean(vinterest),
              sd = sd(vinterest),
              cv = raster::cv(vinterest),
              se = sd / sqrt (length(vinterest))) %>%
    inner_join(topo, by="nie_malla_modi_id") %>%
    inner_join(xycentroides, by="nie_malla_modi_id") %>%
    inner_join(basin, by="nie_malla_modi_id")








ggplot(rawdata, aes(x=fecha, myndvi)) + geom_boxplot() 


# Create variables of year and month 
# Apply scale factor https://lpdaac.usgs.gov/dataset_discovery/modis/modis_products_table/mod13q1 
rawdata <- rawdata %>% 
  mutate(myevi = evi * 0.0001,
         year = lubridate::year(fecha),
         month = lubridate::month(fecha))

# Create annual evi by pixel 
eviyear <- rawdata %>% 
  group_by(iv_malla_modi_id, year) %>%
  summarise(evi = sum(myevi[myevi >=0])) %>%
  mutate(season=0)


# Create seasonal evi 

# Julian date 
# >81 <=173 --> spring (1)
# >173 <=265 --> summer (2)
# > 265 <=356 --> autum (3)
# > 356 and < 81 --> winter (4)
# Get julian day of limits of the season
sp <-lubridate::yday(as.Date("2000-03-21"))
su <- lubridate::yday(as.Date("2000-06-21"))
au <-  lubridate::yday(as.Date("2000-09-21"))
wi <- lubridate::yday(as.Date("2000-12-21"))
season_julian <- c(sp,su,au,wi)

eviseason <- rawdata %>%
  mutate(jday=lubridate::yday(fecha)) %>%
  select(iv_malla_modi_id, year, myevi, jday) %>% 
  mutate(season = ifelse(jday > 81 & jday <= 173, 1,
                        ifelse(jday > 173 & jday <= 265, 2, 
                               ifelse(jday > 265 & jday <= 356, 3, 4)))) %>%
  group_by(iv_malla_modi_id, year, season) %>%
  summarise(evi = sum(myevi[myevi >=0]))


evidf <- rbind(eviyear, eviseason)

evidf <- evidf %>% 
  mutate(seasonF = ifelse (season == 0, 'annual',
                           ifelse(season == 1, 'spring',
                                  ifelse(season == 2, 'summer',
                                         ifelse(season == 3, 'autumn', 'winter')))))



# Add coordinates and pob 
evi_aux <- rawdata %>% select(iv_malla_modi_id, lng, lat, poblacion) %>%
  group_by(iv_malla_modi_id) %>% unique()


# Join dataframes 
evi <- evidf %>% inner_join(evi_aux, by="iv_malla_modi_id") 

# Export evi dataframe
write.csv(evi, file=paste(di, "/data/evi_attributes_all.csv", sep=""), row.names = FALSE)
```